Manuscript analyses

### 2024-01-04 cilta_cel/Manuscript analyses.Rmd
Updates

  mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
  # Create site variable
  mutate(site = case_when(
    str_detect(pt_identifier, "MCC")               ~ "Moffitt",
    str_detect(pt_identifier, "CCT")               ~ "Stanford",
    str_detect(pt_identifier, "KUMC")              ~ "KUMC",
    str_detect(pt_identifier, "MDA")               ~ "MD Anderson?",
    str_detect(pt_identifier, "Utah")              ~ "Utah"
  )) %>%
  # Suboptimal is NA
  mutate(across(c(#"bm_plasma_cell_percent_at_pre_ld",
                  "high_marrow_burden_50_percent",
                  contains("normo_hypo_hyper"),
                  contains("fibrosis"),
                  contains("dysplasia"),
                  "b2_microglobulin_day_180"), 
                ~ str_replace(., "Suboptimal", NA_character_))) %>%
  # Are numerical - also remove "Suboptimal"
  mutate(across(c(starts_with("marrow_fibrosis"),
                  starts_with("ldh_")
                  ), 
                ~ as.numeric(.))) %>%
  mutate(across(c("response_to_bridging_chemotherapy"), 
                ~ str_replace(., "Not evaluable", NA_character_))) %>% 
  # Convert 0/1 to No/Yes
  mutate_at(c("infection_yes_1_no_0",
              "severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0",
              # "bm_plasma_cell_percent_at_pre_ld",
              # "high_marrow_burden_50_percent",
              # "ECOG > or = 2? (Yes, No)",
              # deletion_17p_prior_to_car_t_infusion_yes_no,
              # "t_4_14_prior_to_car_t_infusion_yes_no",
              # "t_14_16_prior_to_car_t_infusion_yes_no",
              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
              # "Bridging Therapy (Yes=1, No=0)",
              # "Received alkylating therapy with bridging (Yes=1, No=0)",
              "need_for_g_csf_post_infus_yes_1_no_0",
              "need_for_ivig_yes_1_no_0",
              "cd34_stem_cell_boost_yes_1_no_0",
              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0"), 
            ~ case_when(
              . == 1                                              ~ "Yes",
              . == 0                                              ~ "No",
              TRUE                                                ~ NA_character_
            )) %>% 
  # Marrow ----
  mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
    marrow_cellularity_baseline_normo_hypo_hyper == "\"patchy\""                 ~ "hyper",
    TRUE                                                          ~ marrow_cellularity_baseline_normo_hypo_hyper
  )) %>%
  mutate(marrow_cellularity_day_30_normo_hypo_hyper = case_when(
    marrow_cellularity_day_30_normo_hypo_hyper == "aplastic"                    ~ "hypo",
    TRUE                                                          ~ marrow_cellularity_day_30_normo_hypo_hyper
  )) %>%
  # Separate variable cellularity
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Variable"                         ~ "Yes"
  ), .names = "is_variable_{.col}")) %>% 
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Pauci"                            ~ "Hypo",
    . == "Variable"                         ~ NA_character_,
    TRUE                                    ~ .
  ))) %>%

@@

```{r Baseline labs}
cart1 <- cart %>% 
  # Baseline labs ----
  mutate(baseline_ferritin_cat = case_when(
    baseline_ferritin_pre_ld >= 400                                      ~ "≥ ULN at LD (≥ 400)",
    baseline_ferritin_pre_ld < 400                                       ~ "Normal (< 400)"
  ), baseline_ferritin_cat = 
    factor(baseline_ferritin_cat, levels = c("Normal (< 400)",
                                             "≥ ULN at LD (≥ 400)"))) %>% 
  mutate(baseline_crp_cat = case_when(
    baseline_crp_pre_ld  >= 0.5                                           ~ "≥ ULN at LD (≥ 0.5)",
    baseline_crp_pre_ld  < 0.5                                            ~ "Normal (< 0.5)"
  ), baseline_crp_cat = 
    factor(baseline_crp_cat, levels = c("Normal (< 0.5)",
                                        "≥ ULN at LD (≥ 0.5)"))) %>% 
  mutate(baseline_B2M = case_when(
    baseline_b2m_pre_ld >= 5.5                                    ~ "≥ 5.5",
    baseline_b2m_pre_ld < 5.5                                     ~ "< 5.5"
  )) %>%
  mutate(cart_cell_dose = case_when(
    cell_dose_million_cells >= 0.7                                ~ "≥ 0.7",
    cell_dose_million_cells < 0.7                                 ~ "< 0.7",
    TRUE                                                          ~ NA_character_
  ),cart_cell_dose = 
    factor(cart_cell_dose, levels = c("≥ 0.7", 
                                      "< 0.7")))
```

@@

  # mutate(access_type = case_when(
  #   access_type == "Femoral"                                    ~ "Non-tunneled",
  #   access_type == "AVF"                                        ~ "Peripheral",
  #   TRUE                                                          ~ access_type
  # )) %>% 
# cart7 <- cart6 %>% 
#   mutate(infection = case_when(
#     notinfused=="YES" ~ NA_character_,
#     notinfused=="NO" & is.na(`Infection Type`) & is.na(`Infection (Yes, No)`) ~ NA_character_,
#     notinfused=="NO" & `Infection Type` == "No" ~ "No", 
#     notinfused=="NO" & `Infection Type` != "No" ~ "Yes",
#     notinfused=="NO" & is.na(`Infection Type`) ~ "No",
#     TRUE ~ NA_character_
#   )) %>%
#   mutate(HLH = case_when(
#     notinfused=="YES" ~ NA_character_,
#     notinfused=="NO" & `HLH/HLH-Like Toxicities?`=="Yes" ~ "Yes",
#     TRUE ~ "No"
#   )) %>%
#   mutate(infection_type = case_when(
#     infection=="No" | is.na(infection) ~ NA_character_,
#     infection=="Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "fungus was unidentified" ~ "Fungal",
#     infection== "Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "E. coli bacteremia and Salmonella GI infection treated with ceftriaxone x 7 days" ~ "Bacterial",
#     infection=="Yes" & `Infection Type`=="bacterial + viral" ~ "Bacterial + Viral",
#     infection=="Yes" & `Infection Type`=="viral" ~ "Viral",
#     infection=="Yes" & `Infection Type`=="All of the above" ~ "Bacterial, Viral, and Fungal",
#     infection=="Yes" & `Infection Type`=="Bacterial; Viral; Bacterial" ~ "Bacterial + Viral",
#     infection=="Yes" & `Infection Type`=="Viral; Bacterial; Bacterial" ~ "Bacterial + Viral",
#     TRUE ~ `Infection Type`
#   )) %>% 
#   mutate(infection_severity = case_when(
#      infection=="No" | is.na(infection) ~ NA_character_,
#      infection=="Yes" & is.na(`Infection Severity (Severe = hospitalization or requiring IV antibiotics)`) ~ NA_character_,
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="severe" ~ "Severe",
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Yes" ~ "Severe",
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="non-severe" ~ "Not severe",
#     infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Non-Severe" ~ "Not severe",
#     TRUE ~ `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`
#   )) %>%
#   mutate(infection_type = factor(infection_type, levels = c("Bacterial", "Fungal", "Viral", "Bacterial + Fungal", "Bacterial + Viral", "Bacterial, Viral, and Fungal")))
```

```{r delayed NT}
cilta <- cart6 %>%
  mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
    is.na(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
                                                                  ~ "No",
    TRUE           ~ other_delayed_non_parkinsonian_neurologic_toxicity_yes_no
  )) %>%
  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
    parkinsonian_neurotoxicity_yes_no == "Yes" & 
      what_non_parkinsonian_neurotoxicity == "Bell's palsy"       ~ "No",
    is.na(parkinsonian_neurotoxicity_yes_no) ~ "No",
    TRUE ~ parkinsonian_neurotoxicity_yes_no
  )) %>%
  mutate(delayed_neuro = case_when(
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" |
      parkinsonian_neurotoxicity_yes_no == "Yes"                  ~ "Yes",
    TRUE                                                          ~ "No"
  )) %>%
  mutate(delayed_neuro_type = case_when(
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (PRES) and parkinsonism" 
                                                                  ~ "Parkinsonian/PRES",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres); progressive multifocal leukoencephalopathy (pml)" 
                                                                  ~ "PRES/PML",
    parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsy")     ~ "Bell's palsy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsey")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "droop")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "PRES")    ~ "PRES", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "dysautonomia") 
                                                                 ~ "Dysautonomia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "plopia")    
                                                                  ~ "Diplopia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "Polyneuropathy") 
                                                                  ~ "Polyneuropathy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) 
```

@@

## Table 1. Patient baseline characteristics
```{r}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, 
         cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
         t_4_14_prior_to_car_t_infusion_yes_no,
         t_14_16_prior_to_car_t_infusion_yes_no,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no) %>% 
  tbl_summary(
    type = list(
      c(agecat, sex, 
        extramedullary_disease_yes_no, high_marrow_burden_50_percent,
        cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
        t_4_14_prior_to_car_t_infusion_yes_no,
        t_14_16_prior_to_car_t_infusion_yes_no,
        bridging_therapy_yes_no, prior_auto_sct_yes_no,
        Prior_bcma_therapy,
        # `Received alkylating therapy with bridging (Yes=1, No=0)`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
        did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
      ~"categorical"),

@@

## Patient characteristics by grade 3+ cytopenia at Day 30
```{r}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
  select(bm_plasma_cell_percent_at_pre_ld,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
         age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, cytogenetics, 
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         gr3_cytopenia_30d) %>% 
  tbl_summary(by = gr3_cytopenia_30d,
              type = list(
                c(extramedullary_disease_yes_no,
                  bm_plasma_cell_percent_at_pre_ld,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  Prior_bcma_therapy,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~"categorical",
                c(bm_plasma_cell_percent_at_pre_ld,
                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
```

>>>>

  mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
  # Create site variable
  mutate(site = case_when(
    str_detect(pt_identifier, "MCC")               ~ "Moffitt",
    str_detect(pt_identifier, "CCT")               ~ "Stanford",
    str_detect(pt_identifier, "KUMC")              ~ "KUMC",
    str_detect(pt_identifier, "MDA")               ~ "MD Anderson?",
    str_detect(pt_identifier, "Utah")              ~ "Utah"
  )) %>%
  # Suboptimal is NA
  mutate(across(c(#"bm_plasma_cell_percent_at_pre_ld",
                  "high_marrow_burden_50_percent",
                  # contains("normo_hypo_hyper"),
                  contains("fibrosis"),
                  contains("dysplasia"),
                  "b2_microglobulin_day_180"), 
                ~ str_replace(., "Suboptimal", NA_character_))) %>%
  # Are numerical - also remove "Suboptimal"
  mutate(across(c(starts_with("marrow_fibrosis"),
                  starts_with("ldh_")
                  ), 
                ~ as.numeric(.))) %>%
  mutate(across(c("response_to_bridging_chemotherapy"), 
                ~ str_replace(., "Not evaluable", NA_character_))) %>% 
  # Convert 0/1 to No/Yes
  mutate_at(c("infection_yes_1_no_0",
              "severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0",
              # "bm_plasma_cell_percent_at_pre_ld",
              # "high_marrow_burden_50_percent",
              # "ECOG > or = 2? (Yes, No)",
              # deletion_17p_prior_to_car_t_infusion_yes_no,
              # "t_4_14_prior_to_car_t_infusion_yes_no",
              # "t_14_16_prior_to_car_t_infusion_yes_no",
              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
              # "Bridging Therapy (Yes=1, No=0)",
              # "Received alkylating therapy with bridging (Yes=1, No=0)",
              "need_for_g_csf_post_infus_yes_1_no_0",
              "need_for_ivig_yes_1_no_0",
              "cd34_stem_cell_boost_yes_1_no_0",
              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0"), 
            ~ case_when(
              . == 1                                              ~ "Yes",
              . == 0                                              ~ "No",
              TRUE                                                ~ NA_character_
            )) %>% 
  # Marrow ----
  mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
    marrow_cellularity_baseline_normo_hypo_hyper == "\"patchy\""                 ~ "hyper",
    TRUE                                                          ~ marrow_cellularity_baseline_normo_hypo_hyper
  )) %>%
  mutate(marrow_cellularity_day_30_normo_hypo_hyper = case_when(
    marrow_cellularity_day_30_normo_hypo_hyper == "aplastic"                    ~ "hypo",
    TRUE                                                          ~ marrow_cellularity_day_30_normo_hypo_hyper
  )) %>%
  # Separate variable cellularity
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Variable"                         ~ "Yes"
  ), .names = "is_variable_{.col}")) %>% 
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Pauci"                            ~ "Hypo",
    . == "Variable"                         ~ NA_character_,
    TRUE                                    ~ .
  ))) %>%

@@

```{r Baseline labs}
cart1 <- cart %>% 
  # Baseline labs ----
  mutate(baseline_ferritin_cat = case_when(
    baseline_ferritin_pre_ld >= 400                                      ~ "≥ ULN at LD (≥ 400)",
    baseline_ferritin_pre_ld < 400                                       ~ "Normal (< 400)"
  ), baseline_ferritin_cat = 
    factor(baseline_ferritin_cat, levels = c("Normal (< 400)",
                                             "≥ ULN at LD (≥ 400)"))) %>% 
  mutate(baseline_crp_cat = case_when(
    baseline_crp_pre_ld  >= 0.5                                           ~ "≥ ULN at LD (≥ 0.5)",
    baseline_crp_pre_ld  < 0.5                                            ~ "Normal (< 0.5)"
  ), baseline_crp_cat = 
    factor(baseline_crp_cat, levels = c("Normal (< 0.5)",
                                        "≥ ULN at LD (≥ 0.5)"))) %>% 
  mutate(baseline_B2M = case_when(
    baseline_b2m_pre_ld >= 5.5                                    ~ "≥ 5.5",
    baseline_b2m_pre_ld < 5.5                                     ~ "< 5.5"
  )) %>%
  mutate(cart_cell_dose = case_when(
    cell_dose_million_cells >= 0.7                                ~ "≥ 0.7",
    cell_dose_million_cells < 0.7                                 ~ "< 0.7",
    TRUE                                                          ~ NA_character_
  ),cart_cell_dose = 
    factor(cart_cell_dose, levels = c("≥ 0.7", 
                                      "< 0.7"))) %>% 
  mutate(access_type = case_when(
    str_detect(access_type, "^C|catheter")                          ~ "Central venous catheter",
    str_detect(access_type, "^P")                                 ~ "Peripheral",
    TRUE                                                          ~ access_type
  ))
```

@@

# cart7 <- cart6 %>% 
#   mutate(infection = case_when(
#     notinfused=="YES" ~ NA_character_,
#     notinfused=="NO" & is.na(`Infection Type`) & is.na(`Infection (Yes, No)`) ~ NA_character_,
#     notinfused=="NO" & `Infection Type` == "No" ~ "No", 
#     notinfused=="NO" & `Infection Type` != "No" ~ "Yes",
#     notinfused=="NO" & is.na(`Infection Type`) ~ "No",
#     TRUE ~ NA_character_
#   )) %>%
#   mutate(HLH = case_when(
#     notinfused=="YES" ~ NA_character_,
#     notinfused=="NO" & `HLH/HLH-Like Toxicities?`=="Yes" ~ "Yes",
#     TRUE ~ "No"
#   )) %>%
#   mutate(infection_type = case_when(
#     infection=="No" | is.na(infection) ~ NA_character_,
#     infection=="Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "fungus was unidentified" ~ "Fungal",
#     infection== "Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "E. coli bacteremia and Salmonella GI infection treated with ceftriaxone x 7 days" ~ "Bacterial",
#     infection=="Yes" & `Infection Type`=="bacterial + viral" ~ "Bacterial + Viral",
#     infection=="Yes" & `Infection Type`=="viral" ~ "Viral",
#     infection=="Yes" & `Infection Type`=="All of the above" ~ "Bacterial, Viral, and Fungal",
#     infection=="Yes" & `Infection Type`=="Bacterial; Viral; Bacterial" ~ "Bacterial + Viral",
#     infection=="Yes" & `Infection Type`=="Viral; Bacterial; Bacterial" ~ "Bacterial + Viral",
#     TRUE ~ `Infection Type`
#   )) %>% 
#   mutate(infection_severity = case_when(
#      infection=="No" | is.na(infection) ~ NA_character_,
#      infection=="Yes" & is.na(`Infection Severity (Severe = hospitalization or requiring IV antibiotics)`) ~ NA_character_,
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="severe" ~ "Severe",
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Yes" ~ "Severe",
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="non-severe" ~ "Not severe",
#     infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Non-Severe" ~ "Not severe",
#     TRUE ~ `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`
#   )) %>%
#   mutate(infection_type = factor(infection_type, levels = c("Bacterial", "Fungal", "Viral", "Bacterial + Fungal", "Bacterial + Viral", "Bacterial, Viral, and Fungal")))
```

```{r delayed NT}
cilta <- cart6 %>%
  mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
    is.na(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
                                                                  ~ "No",
    TRUE           ~ other_delayed_non_parkinsonian_neurologic_toxicity_yes_no
  )) %>%
  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
    parkinsonian_neurotoxicity_yes_no == "Yes" & 
      what_non_parkinsonian_neurotoxicity == "Bell's palsy"       ~ "No",
    is.na(parkinsonian_neurotoxicity_yes_no) ~ "No",
    TRUE ~ parkinsonian_neurotoxicity_yes_no
  )) %>%
  mutate(delayed_neuro = case_when(
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" |
      parkinsonian_neurotoxicity_yes_no == "Yes"                  ~ "Yes",
    TRUE                                                          ~ "No"
  )) %>%
  mutate(delayed_neuro_type = case_when(
    what_non_parkinsonian_neurotoxicity == "Aidp"                 ~ "Polyneuropathy",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (PRES) and parkinsonism" 
                                                                  ~ "Parkinsonian/PRES",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres); progressive multifocal leukoencephalopathy (pml)" 
                                                                  ~ "PRES/PML",
    parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsy")     ~ "Bell's palsy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsey")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "droop")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "PRES")    ~ "PRES", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "dysautonomia") 
                                                                 ~ "Dysautonomia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "plopia")    
                                                                  ~ "Diplopia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "Polyneuropathy") 
                                                                  ~ "Polyneuropathy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) 
```

@@

## Table 1. Patient baseline characteristics
```{r}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(os_from_infusion_months, age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, 
         cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
         t_4_14_prior_to_car_t_infusion_yes_no,
         t_14_16_prior_to_car_t_infusion_yes_no,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no) %>% 
  tbl_summary(
    type = list(
      c(agecat, sex, 
        extramedullary_disease_yes_no, high_marrow_burden_50_percent,
        cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
        t_4_14_prior_to_car_t_infusion_yes_no,
        t_14_16_prior_to_car_t_infusion_yes_no,
        bridging_therapy_yes_no, prior_auto_sct_yes_no,
        Prior_bcma_therapy,
        # `Received alkylating therapy with bridging (Yes=1, No=0)`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
        did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
      ~"categorical"),

@@

## Patient characteristics by grade 3+ cytopenia at Day 30
```{r}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
  select(bm_plasma_cell_percent_at_pre_ld,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
         os_from_infusion_months, age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, cytogenetics, 
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         gr3_cytopenia_30d) %>% 
  tbl_summary(by = gr3_cytopenia_30d,
              type = list(
                c(extramedullary_disease_yes_no,
                  bm_plasma_cell_percent_at_pre_ld,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  Prior_bcma_therapy,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~"categorical",
                c(bm_plasma_cell_percent_at_pre_ld,
                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
```
